\section{Conclusion} \label{conclusion}
In this experiment, we built upon existing empirical literature
and analyzed how QV aligns with participants' true preferences compared with Likert surveys.
We examined the transferability of QV when applied to the HCI domain, and we demonstrated the impact of different voice credits.

\section{Limitation and Future Work} \label{future}

\subsection{Limitation}
We identified two limitations in this study, 
mainly focused on the second experiment.
First, participants in the buyback group
only have one shot.
Some participants did indicate that
they would change what they bought
when they completed the quiz.
It requires further examination
if the first attempt should be considered as one's true preference
or the edited buyback values.

In addition, we are also aware that
designing a between-subject study 
weakened the generalizability 
of the second experiment.
However, we are also aware possible confounds
if both the Likert Group or the QV group completed the buyback.
The buyback will be highly correlated with the survey responses
and it is difficult to issue another task
like in the first experiment
to disconnect participant's cognitive attention
from the video experience, the survey to the buyback.

\subsection{Behavior when casting votes} % slightly boring
It is important to point out that Despite only occurring once (\texttt{P1d659}), we think the term ``voting'' might motivate participants to consider how a collective decision was made.
%scenere voting might not happen in QV?, mentioned in the voting chapter
This participant mentioned ``[\textellipsis] I thought a lot of people would probably support faith and spiritual ecatagory  so I watned to try to counterbalance that by voting against it.'' The participants are willing to pay the cost by devoting fewer votes for issues they care and vote against specific ballots. This behavior is not possible in a Likert survey. This requires further experiments to understand how people's mental model works when voting under QV. \par 

\subsection{Ease of use}
In addition, we do not have enough understanding of the level of usability of QV from two aspects.
First, we are not sure how easy it is for participants to understand QV.
In our experiment, participants are far more familiar with Likert-scaled surveys compared to QV, placing a lighter cognitive load.
We acknowledge that participants need additional time and effort to understand and utilize QV throughout our experiment, yet, it is unclear if education level and prior experiences impact participants' understanding of QV and their final choices.
Second, we do not know if there exists diminished effectiveness of QV if there are large amounts of options, meaning selecting a few over hundreds of options.

\subsection{Interface and medium}
Finally, one crucial unanswered question lies in the medium and interface that QV should be deployed.
It is almost certain that QV will be hard to present on paper since it requires complex calculations. 
Besides, we did not examine if there are differences when voting on a laptop or a handheld device.
We also had not uncovered whether different interface designs, visualization, and additional information impact the performance of QV.

